---
title: "Report Title"
date: "`r Sys.Date()`"
author: Author Name
date-format: "D MMMM YYYY"
format:
  html:
    # Table of Contents options
    toc: true
    toc-depth: 3
    toc-expand: true
    toc-location: left
    toc-title: Table of Contents
    number-sections: false
    number-depth: 3
    # Render options
    theme: cosmo
    css: css/theme.css   # Replace with the directory of your css file (e.g., theme.css within 'CSS' folder)
    anchor-sections: false
    html-math-method: katex
    # Code options
    code-tools:
      source: false
      toggle: false
      caption: none
    code-fold: false
    # code-summary: "Show code"
    embed-resources: true
    standalone: true
    # URL options
    link-external-icon: false
    link-external-newwindow: true
    # Reference options
    citations-hover: true
    footnotes-hover: true
    # Callout options
    callout-appearance: simple
    callout-collapse: true
    # Caption options
    cap-location: bottom
    # Title options
    title-block-banner: '#005EB8'
    backgroundcolor: '#f0f4f5'
    # Set font
    mainfont: 'Open Sans'
      
execute:
  echo: false
  cache: true              # Cache results
  warning: false           # Do not include warnings in rendered output
  error: false             # Do not include errors in the output
  feeze: auto              # Re-compute previously generated computational output only in case their source file changes
crossref:
  fig-title: '**Figure**'
  fig-labels: arabic
include-after-body: "html/footer.html"
---

```{r}
#| label: load-libraries
#| warning: false
#| output: false
#| echo: false


# Load the required library
library(ggplot2)
library(plotly)
library(tidyverse)
library(DT)

```

# Chapter 1
## Subtitle

Text.

<!-- start of chart tabset -->

:::: panel-tabset

<!-- make new tabs with ## -->
## Chart

```{r}
#| label: mtcars-plot

# Add your chart here
#-------------------------------------------------------------------------------

# Load the mtcars dataset
data(mtcars)

# Create a scatter plot using plotly
fig <- plot_ly(data = mtcars, x = ~wt, y = ~mpg, type = "scatter", mode = "markers") %>%
  layout(
    title = "Miles per Gallon vs. Weight",
    xaxis = list(title = "Weight (1000 lbs)"),
    yaxis = list(title = "Miles per Gallon")
  )

# Display the plot
fig

```

<!-- make new tabs with ## -->

## Table

```{r}
#| label: mtcars-data

# Add your table here
#-------------------------------------------------------------------------------

# Load the mtcars dataset
data(mtcars)


# Print the table

datatable(mtcars, extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf'),
                           pageLength=5, 
                           lengthMenu=c(3,5,10) ))
```


## More information

Text.

::::

<!-- end of chart tabset -->

::: {.callout-tip}
## Trends

The scatter plot displays the relationship between the weight of a vehicle (in thousands of pounds) on the x-axis and its miles per gallon (MPG) on the y-axis. 

- Trend 1
- Trend 2
- Trend 3


:::


# Chapter 2
## Subtitle
Text.

<!-- start of chart tabset -->

::: {.panel-tabset }

## Chart
```{r}
#| label: rand-plot

# Generate two sets of random numbers
data1 <- rnorm(50)
data2 <- rnorm(50, 1)

# Create a boxplot with Plotly
fig <- plot_ly(type = "box") %>%
  add_trace(y = ~data1, name = "Dataset 1") %>%
  add_trace(y = ~data2, name = "Dataset 2")

# Display the boxplot
fig

```

## Table
```{r}
#| label: rand-data

# Combine the data into a data frame
data_df <- data.frame(
  "Dataset 1" = data1,
  "Dataset 2" = data2
)

# Display the data in a DT table

datatable(data_df, extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf'),
                           pageLength=5, 
                           lengthMenu=c(3,5,10) ))
```

## More information

Text.

:::

<!-- End of chart tabset -->

::: {.callout-tip}
## Trends

The boxplots visualize the distribution of randomly generated numbers in two different datasets.

- Trend 1
- Trend 2
- Trend 3


:::






